article title

### 2022-07-20 article.tex
Refactor citations for authoryear style

% useful for the bibliography
\usepackage[style=numeric]{biblatex}
\addbibresource{pilon_gilles.bib}

@@

% The definitive book on MSA is by Wheeler \cite{wheeler2006}. The definitive book on SPC is by Wheeler \cite{wheeler2004}. The original article on Taguchi indices was by Russell Boyles \cite{boyles1991}. A very good article on the $C_\text{pm}$ index is found in Chen et.al. \cite{chan1988}. Gunter \cite{gunter1989}.

Here is a single citation without prenote and postnote. The definitive book on MSA is by Wheeler \cite{wheeler2006}.

Here is a single citation with prenote only. The definitive book on SPC is by \cite[Wheeler][]{wheeler2006}.

Here is a single citation with prenote and postnote. For further details on $C_\text{pm}$, \cite[see][pages 1-10]{chan1988}.

>>>>

% useful for the bibliography
\usepackage[style=authoryear]{biblatex}
\addbibresource{pilon_gilles.bib}

@@

Here is a single citation without prenote and postnote. There is a definitive book on MSA (\cite{wheeler2006}).

Here is a single citation with prenote only. There is a definitive book on SPC (\cite[see][]{wheeler2006}).

Here is a single citation with postnote only. $C_\text{pm}$ is a complex subject (\cite[][pages 1-10]{chan1988}).
